\chapter{Functional Requirements}

\section{Introduction}
In this document the requirements for assignment 5 will be stated. In this sprint we will add several novel features to the game. \noindent The requirements are presented using the \fnurl{MoSCoW Model}{https://en.wikipedia.org/wiki/MoSCoW_method}.

\section{Must Have}
\begin{itemize}
\itemsep0em
\item The game shall have a final level with a boss to play against. 
\item The players shall be able to register their names when they start playing.
\item The high-scores for each player shall be saved. 
\item The player shall be able to return to the menu when playing a game. 
\item The player shall be able to access a settings-panel from within the menu. 
\item The player shall be able to turn off the music in the settings-menu. 
\item The settings a player chooses in the settings-menu shall be saved so that when the game is loaded again, the same settings are applied. 
\end{itemize}

\section{Should Have}
\begin{itemize}
\itemsep0em
\item The boss in the final level should have a special ability as opposed to the normal monsters (such as being able to shoot).
\item All high-scores shall be visible from within the menu. 
\item The final level with the boss shall have a different background music. 
\item The players shall be able to set their names once in the menu, which will be used afterwards every time a game is started.  
\end{itemize}

\section{Could Have}
\begin{itemize}
\itemsep0em
\item The player shall be able to change the keys used to control a sprite from within settings-menu. 
\item Special sounds shall be added for events like 'shooting a bubble' and 'killing a monster'. 
\end{itemize}

\section{Won't Have}
\begin{itemize}
\itemsep0em
\item The high-scores will be saved in an online database. 
\end{itemize}