\chapter{Functional Requirements}

\section{Introduction}
In this document the requirements for assignment 2 will be stated. There will be improvements to the code, as well as new functionalities. \noindent This will be done using the \fnurl{MoSCoW Model}{https://en.wikipedia.org/wiki/MoSCoW_method}.

\section{Must Have}
\begin{itemize}
\itemsep0em
\item The player must be able to fall through the floor.
\item The player must reappear after falling through the floor at the corresponding square in the ceiling.
\item The monsters must be able to fall though the floor.
\item The monsters must reappear after falling through the floor at the corresponding square in the ceiling.
\item The monsters must be able to jump.
\item The monsters must be able to jump and move around randomly.
\item The player must be able to jump in a more natural way, so a decrease in speed when the player jumps.
\item The player must be able to fall in a more natural way, so an increase in speed when the player falls.
\item The monsters must be able to jump in a more natural way, so a decrease in speed when the monster jumps.
\item The monsters must be able to fall in a more natural way, so an increase in speed when the monster falls.
\item The bubbles must be able to float to the top of the screen.
\item The bubbles must disappear after a period of time.
\item The player must be able to jump on a bubble, and use it like a lift.
\end{itemize}

\section{Should Have}
\begin{itemize}
\itemsep0em
\item The bubbles should be able to float through the ceilings, but stop at the top ceiling.
\item The player should be able to jump on a bubble, and use it like a trampoline.
\end{itemize}

\section{Could Have}
\begin{itemize}
\itemsep0em
\item The player could be able to jump through the ceiling.
\item The player could reappear after jumping through the ceiling at the corresponding square in the floor.
\item The monster could be able to jump through the ceiling.
\item The monster could reappear after jumping through the ceiling at the corresponding square in the floor.
\item The bubbles could pop when they disappear.
\item The game could play music when played.
\end{itemize}

\section{Won't Have}
\begin{itemize}
\itemsep0em
\item The monsters won't be able to follow the players movement.
\end{itemize}